---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
```{r echo=TRUE}
library(tidyverse)

activity <- read.csv("activity.csv")

# change type of steps to numeric and replace NA with 0
activity$steps <- as.numeric(activity$steps) %>%
  replace_na(0)

# ensure date is interpreted as a Date
activity$date <- as.Date(as.character(
  strptime(activity$date, "%Y-%m-%d")))
  
```


## What is mean total number of steps taken per day?
```{r echo=TRUE, fig.width = 6, fig.height = 4}

steps <- activity %>%
  group_by(date) %>%
  summarise(total = sum(steps))

hist(steps$total, breaks = "FD",
     main = "Distribution of Total Steps per Day",
     xlab = "Total Steps")

steps_mean <- mean(steps$total, na.rm=TRUE)
steps_median <- median(steps$total, na.rm=TRUE)

```
Using the functions "mean()" and "median()" on the calculated dataframe "steps", over the column "total". We find that (rounded down to nearest integer)

- Mean = 9354
- Median = 10395

## What is the average daily activity pattern?
```{r echo=TRUE, fig.width = 6, fig.height = 4}
```


## Imputing missing values
```{r echo=TRUE, fig.width = 6, fig.height = 4}
```


## Are there differences in activity patterns between weekdays and weekends?
```{r echo=TRUE}
```